---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## alphabetr
`alphabetr` implements the ALPHABETR (algorithm for pairing alpha-beta T cell receptors) algorithms for obtaining TCR sequence pairs. This approach determines CDR3A/CDR3B pairs from high-throughput sequencing data from repeated samples of antigen-specific T cell populations. 

With `alphabetr`, you can

* Determine CDR3A/CDR3B pairs
* Determine dual TCR-alpha clones and clones that share CDR3A or CDR3B sequences
* Estimate clonal frequencies

You can install

* the latest version released on CRAN with
```{r eval = FALSE}
install.packages("alphabetr")
```
* the latest development version found on github with
```{r eval = FALSE}
if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}
devtools::install_github("edwardslee/alphabetr")
```

If you encounter any bugs, please file an [issue](https://github.com/edwardslee/alphabetr/issues).

## More information
Please see [our paper in PLOS Computational Biology](http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005313) for more details about the algorithm and how it was tested (DOI: 10.1371/journal.pcbi.1005313).
